---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=TRUE, echo=FALSE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=10.5, fig.width=10.5)
library(printr)
read_chunk("../../code/cavm_flam_dist.R")
```

```{r setup2}
```

```{r plot_setup}
```

##
##
## Exploratory plots of marginal and conditional flammability distributions.

Each plot is broken out by vegetation class within the CAVM tundra region as well as each of three component classes, shrub, graminoid, and wetland tundra.
Currently this is only done for CAVM vegetation classes - shrub, graminoid, and wetland tundra - hence the script name.
Non-CAVM, i.e., boreal forest, is ignored by this script.

### Marginal distribution

The first plot shows a density function proportional to joint probability distribution for flammability in time and space,
marginalized with repsect to time. The time period is 1950 - 2013. The second plot is the same, but truncated to a maximum of 0.16 flammability.

```{r plot01a}
```

```{r plot01b}
```

### Conditional distribution

This plot shows multiple overlapping spatial flammability distributions conditioned on each year, also truncated at 0.16.

```{r plot02}
```

The table below provides distribution quantiles by vegetation class.

```{r table01}
```
