---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=TRUE, tidy=TRUE, message=FALSE, warning=FALSE, fig.height=9, fig.width=13.5)
read_chunk("../../code/fseMLE.R")
```

##
##
## fseMLE.R

The `fseMLE.R` script performs exploratory data analysis followed by maximum likelihood estimation of fire size distributions based on historical observations and ALFRESCO simulation outputs.
Currently under development using Noatak region data only.
Preliminary EDA plots available.

## R code and results

### Setup

```{r setup}
```

##
##
### Exploratory data analysis

#### Fire count by vegetation class: Noatak

```{r fc_noa_veg}
```

#### Fire count by vegetation class: Statewide

```{r fc_sw_veg}
```

#### Fire count by decade: Noatak shrub

```{r fc_noa_shrub_dec}
```

#### Fire count by decade: Statewide forest

```{r fc_sw_forest_dec}
```


```{r eda_pngs, echo=FALSE}
```


##
##
### Maximum likelihood estimation

#```{r mle}
#```
