---
output:
  html_document:
    toc: false
    theme: spacelab
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/gbm_flam_maps.R")
```

##
##
## gbm_flam_maps.R

The `gbm_flam_maps.R` script creates gradient boosting machine (GBM) model-based, or boosted regresion model-based, vegetation flammability maps.
It loads a given **R** workspace file created by `gbm_flam_prep.R`.
Other inputs include GBM models built on vegetation-specific, aggregate regional climate data.
These monthly maps are used as inputs to ALFRESCO in lieu of basic monthly temperature and precipitation maps.

## R code

### Setup

```{r setup}
```

### Prep function
```{r func_prep}
```

### Prediction function
```{r func_predict}
```

### Write function
```{r func_write}
```

### Run predictions and save flammability maps

```{r run}
```

### Save PNG plots of flammability maps
```{r plot}
```
