---
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/meanTPbyVegClass_CRU31.R")
```

##
##
## meanTPbyVegClass_CRU31.R

The `meanTPbyVegClass_CRU31.R` script calculates mean temperature and precipitation over all grid cells in a CRU 3.1 map layer conditional of vegetation class using a given vegetation classification map.
These vegetation-specific climate means are used as variables in gradient boosting machine (GBM), or generalized boosted regression modeling.
The resulting GBM models are used to develop climate-driven, vegetation-mediated flammability maps with a nonlinear fire response to climate for use in ALFRESCO in place of basic temperature and precipitation maps.

## R code

### Setup

```{r setup}
```

### Function

```{r func_means}
```

### Run

```{r run}
```

### Save outputs

```{r save}
```
